Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Updated text with new orphan figure

Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar--\mpeak$ relation using {\em all} subhalos, including those that may be disrupted. We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe. We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.

@@

{\color{blue} Include new plot of clustering ratios without orphans.}
%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.

>>>>

Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted. We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe. We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.

@@

The impact of our orphan treatment on $\mstar-$threshold clustering is shown in Figure \ref{fig:baseline_sham_clustering} in the main body of the text. We show the impact on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_clustering_ratios}. Encouragingly, when tuning $\mathcal{F}_{\rm orphan}$ so that the overall $\mstar-$threshold clustering is roughly correct (as in Figure \ref{fig:baseline_sham_clustering}), the same level of tuning is required for a successful prediction of $\rhalf-$dependent clustering. This figure gives quantitative motivation for the program described in \S\ref{subsec:future} to jointly constrain the satellite fraction $F_{\rm sat}(\mstar)$ together with models for galaxy size.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/clustering_ratios_orphan_impact.pdf}
\caption{
Points with error bars as well as the black curves are the same as in Figure \ref{fig:clustering_ratio_upshot}. Red curves show predictions for the $\rhalf-$clustering ratios of the $\rvir-$based model, but excluding orphan subhalos. 
}
\label{fig:orphan_clustering_ratios}
\end{figure}
%-----------------------------------------------------------------------------------------------------
%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.
